%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Nickson}{Kaigi}
\title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{6677-00100, Nairobi Kenya}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+254 724 708 852}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{nickaigi@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{http://nickaigi.github.io/}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\small{Software engineer, with expansive knowledge of Python and JavaScript. Driven individual, with a background in Computer Science and vast experience developing and shipping software and data products. Currently pursuing a Master's of Science Degree in Computation Intelligence at The University of Nairobi.}

\section{Experience}

\vspace{6pt}

\begin{itemize}

\item{\cventry{November 2021 -- July 2022}{Full Stack Engineer}{Sum Software Limited}{}{}{\vspace{3pt}Was an engineer working on the Sumfully software. Sumfully is a Amazon Profit Analytics and Inventory Management Tool.}}

\vspace{6pt}

\item{\cventry{December 2021 -- January 2022}{Technical Consultant}{World Bank}{}{}{\vspace{3pt}Working with The Data and Evidence for Justice Reform (DE JURE) and Development Impact Evaluation (DIME) units in the development of data-driven applications with the intention of studying, improving efficiency, quality and access to justice in developing countries.}}

\vspace{6pt}

\item{\cventry{June 2015 -- October 2021}{Lead Developer}{Maxum Data}{}{}{\vspace{3pt}Lead developer in charge of back end development, server setup and maintenance on AWS, Django templating, Nginx and uWSGI configuration. I was responsible for design and development of the in-house analysis and reporting tool. I wrote Lua scripts that acted as an interface to a custom installation of Freeswitch. I wrote bash scripts that would analyse the production databases for changes that met a predetermined threshold, resulting in a call to action when the changes met the threshold. Wrote Python scripts that analysed spending on toll free and regular phone numbers and created monthly billing reports.}}

\vspace{6pt}

\item{\cventry{June 2015 -- September 2015}{Senior Python Developer}{Domains Bot}{}{}{\vspace{3pt}Senior developer in charge of back end development, server setup and maintenance on AWS, Django templating, Nginx and uWSGI configuration.}}

\vspace{6pt}

\item{\cventry{May 2014 -- January 2015}{Senior Python Developer}{SunUp Financial LLC (Balance Credit)}{}{}{\vspace{3pt}Senior developer in charge of back end development, server setup and maintenance on AWS, Django templating, Nginx and uWSGI configuration.}}

\vspace{6pt}

\item{\cventry{July 2013 -- April 2014}{Senior Python Developer}{Soko}{Nairobi}{}{\vspace{3pt}Senior developer in charge of UX, Python and Android development for the suite of open source and enterprise tools that the company provided.}}

\vspace{6pt}

\item{\cventry{December 2012 -- July 2013}{Senior Python Developer}{Sweet Relish}{}{}{\vspace{3pt}Python developer working with Django and jQuery mobile to deliver a mobile friendly version of the website.}}

\vspace{6pt}


\item{\cventry{September -- November 2012}{Lead Software Developer}{Code Painters}{}{}{\vspace{3pt}Lead developer responsible for product development of various Python Django based web applications.}}

\vspace{6pt}

\item{\cventry{April 2012}{Software Developer}{Apartment Rentals}{}{}{\vspace{3pt}Python Django developer responsible for providing end-to-end Programming support.}}

\vspace{6pt}

\item{\cventry{March -- April 2012}{Python/ Django Developer}{MANteresting}{}{}{\vspace{3pt}Python Django developer responsible for design and implementation of a REST based API.}}

\vspace{6pt}

\item{\cventry{September -- December 2011}{Software Engineer (intern)}{Alliance Technologies}{Nairobi}{}{\vspace{3pt}Engineering intern responsible for extending the A1ERP data dictionary and developing an android based prototype of the ERP.}}

\end{itemize}


\section{Education}

\vspace{5pt}

\subsection{Academic Qualifications}

\vspace{5pt}

\begin{itemize}

\item{\cventry{2014--Present}{MSc Computation Intelligence }{University of Nairobi}{Nairobi, Kenya}{\textit{Completed Coursework. Thesis in Progress}}{}}

\item{\cventry{2008--2012}{BSc Computer Science }{Jomo Kenyatta University of Agriculture and Technology}{Nairobi, Kenya}{\textit{Second Class Honors, Upper Division}}{}}  % arguments 3 to 6 can be left empty

\item{\cventry{2003--2006}{KCSE}{Menengai High School }{Nakuru, Kenya}{}{}}

\end{itemize}

\vspace{2pt}

%\subsection{Notable Projects}

%\vspace{5pt}

%\begin{itemize}

%\item{\textbf{Masters Project (Ongoing):} \textit{'Development of an Intelligent Humanoid Robot'}

%\vspace{3pt}

%\small{I was part of the team that...}}

%%\newpage

%\end{itemize}

\section{Technical and Personal skills}

\vspace{6pt}

\begin{itemize}

\item \textbf{Programming Languages:} Proficient in: Python, JavaScript, \TeX \\ Also basic ability with: C/C++.

\vspace{6pt}

%\item \textbf{Industry Software Skills:} SolidWorks (Advanced), Matlab (Advanced), Ansys (Intermediate),  LTspice (Intermediate), Most MS Office products including MS project and MS access (Advanced).

%\vspace{6pt}

\end{itemize}

\section{Interests and extra-curricular activity}

\vspace{6pt}

\begin{itemize}

\item{I enjoy the game of Chess}

\vspace{6pt}

\item{I am an avid reader of fiction, high fantasy, biographical, and historical/historical fiction books}

\end{itemize}

\section{References}

\vspace{6pt}
 
\begin{itemize}

\item{Up to 3 references available on request}

\end{itemize}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}

%% end of file `main.tex'.
