\documentclass[11pt]{article} % fontsize 10pt/11pt/12pt
\usepackage[margin=1in, a4paper]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{calc}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={Nickson Kaigi - Resume},
    pdfencoding=auto,
    psdextra,
    pdfauthor={Nickson Kaigi},
    pdfsubject={Software Engineer Resume},
    pdfkeywords={Python, Django, PostgreSQL, AWS, React},
    bookmarksopen=true,
    bookmarksdepth=2,
}

\setcounter{secnumdepth}{0} % remove section numbering
\titlespacing{\subsection}{0pt}{*0}{*0} % remove vertical spacing above and below
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\large\itshape}
\setlist[itemize]{
    noitemsep,          % No extra space between items
    topsep=4pt,         % Space above/below list
    leftmargin=1.5em    % Indentation
}

\newcommand \techstack [1]
    {\small\textit{Tech Stack: {#1}}} % New tech stack command

\pagestyle{empty} % remove page number
\pdfgentounicode=1


\begin{document}

\begin{center}
    \begin{minipage}{0.5\textwidth}
    {\Huge\bfseries
        \texorpdfstring{Nickson Kaigi}{Nickson Kaigi}
        } \\ \medskip
        Software Engineer
    \end{minipage} \hfill
    \begin{minipage}{0.4\textwidth}
        \raggedleft
        Email: \href{mailto:nickaigi@gmail.com}{nickaigi@gmail.com} \\
        Mobile: +254 724 708 852 \\
        LinkedIn: \href{https://www.linkedin.com/in/nickson-kaigi/}{linkedin.com/in/nickson-kaigi} \\
        GitHub: \href{https://github.com/nickaigi}{github.com/nickaigi}
    \end{minipage}
\end{center}

\section{Professional Profile}
%============================%
\begin{itemize}
    \item Results-driven \textbf{Full-Stack Python Engineer} with decade of experience building \textbf{high-performance SaaS solutions}
    \item Specialized in \textbf{Database optimization}, \textbf{CI/CD pipelines}, and \textbf{API integration}
    \item Adept at leading technical projects from concept to deployment using \textbf{Agile methodologies} and \textbf{cloud architecture}
\end{itemize}

\section{Technical Expertise}
%===========================%
\begin{description}
    \item[Backend] Python, Django, FastAPI, Django REST Framework, Celery.
    \item[Frontend] React, Next.js, jQuery(legacy).
    \item[Databases] PostgreSQL, MySQL.
    \item[Cloud/DevOps] AWS, Docker, Jenkins, GitHub Actions.
\end{description}

%======== Work Experience Section ========
\section{Experience}

% SKUify Limited
\subsection{SKUify Limited \hfill United Kingdom - Remote}
\subsubsection{Full Stack Engineer \hfill  Dec 2023 -- Dec 2024}
\begin{itemize}
    \item \textbf{Database Optimization:} Partitioned PostgreSQL tables for high-volume datasets, reducing query latency by 30\% and improving API response times by 50\%.
    \item \textbf{Seller Analytics:} Built dashboards integrating Amazon SP-API, automating sales reports for 500+ users and enhancing decision making.
    \item \textbf{CI/CD:} Maintained Jenkins workflows for zero-downtime deployments, improving release efficiency by 20\%.
\end{itemize}
\techstack{Python, Django, React, PostgreSQL, Digital Ocean, Celery, Jenkins}
\vspace{0.8em}

% FreeCast Inc
\subsection{FreeCast Inc \hfill United States of America - Remote}
\subsubsection{Back-end Engineer \hfill  Sep 2022 -- Nov 2023}
\begin{itemize}
    \item \textbf {API Performance:} Migrated REST APIs from Django REST Framework to FastAPI, increasing throughput by 40\% (RPS) and reducing latency.
    \item \textbf {Microservices Architecture:} Deployed serverless endpoints on AWS Lambda using Docker containerization, cutting infrastructure costs by 25\%.
    \item \textbf {Agile Development:} Collaborated cross-functionally in 2-week sprints to deliver features.
\end{itemize}
\techstack{Python, FastAPI, Django, AWS Lambda, MySQL, Docker, GitHub Actions}
\vspace{0.8em}

% SumSoftware Limited
\subsection{Sum Software Limited \hfill United Kingdom - Remote}
\subsubsection{Full Stack Engineer \hfill  Nov 2021 -- Jul 2022}
\begin{itemize}
    \item \textbf{Feature Development:} Built the "Journey" component of the Sumfully SaaS, streamlining inventory management for Amazon and Arbitrage sellers.
    \item \textbf{Report Generation:} Developed custom Python scripts that generated report data from Amazon Marketplace Web Service (MWS) that was SOAP based API.
\end{itemize}
\techstack{Python, Django, Django REST Framework, React, PostgreSQL, Celery, Jenkins}
\vspace{0.8em}

% World Bank Group
\subsection{World Bank Group \hfill United States of America - Remote}
\subsubsection{Technical Consultant \hfill  Dec 2021 -- Jan 2022}
\begin{itemize}
    \item \textbf{Legal Analytics Prototype:} Developed a tool to analyze 10,000+ court judgments for bias detection using Python/Django.
\end{itemize}
\techstack{Python, Django, React, MySQL}
\vspace{0.8em}

% Maxum Data Limited
\subsection{Maxum Data Limited \hfill New Zealand - Remote}
\subsubsection{Lead Developer \hfill  Jun 2015 -- Oct 2021}
\begin{itemize}
    \item \textbf{mPort System:} Built mobile number portability tracker that facilitated seamless network operator migration for 10,000+ users.
    \item \textbf{Tool-Free Number Search: } Created a search tool increasing toll-free number adoption by 35\%.
    \item \textbf{Customization} Wrote Lua scripts for FreeSwtich, reducing network team's setup and customization time by 50\%
\end{itemize}
\techstack{Python, Django, MySQL, Lua}
\vspace{0.8em}

% Domains Bot
\subsection{Domains Bot \hfill Italy - Remote}
\subsubsection{Senior Python Engineer \hfill  Jun 2015 - Sep 2015}
\begin{itemize}
    \item Redesigned database schema, improving query speed by 10\%.
\end{itemize}
\techstack{Python, Django, MySQL}
\vspace{0.8em}

% SunUp Financial LLC
\subsection{SunUp Financial LLC \hfill United States - Remote}
\subsubsection{Senior Python Engineer \hfill  May 2014 -- Jan 2015}
\begin{itemize}
    \item Worked on the development of the "Balance Credit" web project that created the on-boarding process for customers of the Company's Pay Day loans product, emphasizing with the design team to enhance user experience.
\end{itemize}
\techstack{Python, Django, MySQL, jQuery}
\vspace{0.8em}

% Soko Inc
\subsection{Soko Inc. \hfill Nairobi, Kenya}
\subsubsection{Senior Python Engineer \hfill  Jul 2013 -- Apr 2014}
\begin{itemize}
    \item \textbf{Mobile App:} Led the development of a Android app for Soko Artisans.
    \item \textbf{REST API:} Participated in REST API development on the project that were used on by the Mobile application.
    \item \textbf{Framework Migration:} Worked on the transition of the Soko web project from Django Framework to the Pyramid Web Framework.
\end{itemize}
\techstack{Python, Django, Django REST Framework, Pyramid Framework, MySQL, Android}
\vspace{0.8em}

% Sweet Relish LLC
\subsection{Sweet Relish LLC \hfill USA, Remote}
\subsubsection{Senior Python Engineer \hfill  Dec 2012 - Jul 2013}
\begin{itemize}
    \item Fixed critical bugs on jQuery Mobile application, enhancing performance.
\end{itemize}
\techstack{Python, Django, MySQL}
\vspace{0.8em}

% Code Painters LLC
\subsection{Code Painters LLC \hfill USA, Remote}
\subsubsection{Lead Engineer \hfill  Sep 2012 - Nov 2012}
\begin{itemize}
    \item Led the development Gym management website that included subscription management and gym session reservation.
\end{itemize}
\techstack{Python, Django, MySQL, jQuery}
\vspace{0.8em}

% Apartment Rentals
\subsection{Apartment Rentals \hfill USA, Remote}
\subsubsection{Python Engineer \hfill  Apr 2012}
\begin{itemize}
    \item Worked on bug fixes to the project
\end{itemize}
\techstack{Python, Django, MySQL, jQuery}
\vspace{0.8em}

% Manteresing LLC
\subsection{MANteresting \hfill USA, Remote}
\subsubsection{Django Developer \hfill  Mar 2012 - Apr 2012}
\begin{itemize}
    \item Led the development of version 1 of MANteresting REST APIs that were used on the mobile version of the project, ensuring adherence to Agile methods.
\end{itemize}
\techstack{Python, Django, REST API, MySQL, jQuery}
\vspace{0.8em}

% Alliance Technologies
\subsection{Alliance Technologies Limited \hfill Nairobi, Kenya}
\subsubsection{Software Engineer - Intern \hfill  Sep 2011 - Dec 2011}
\begin{itemize}
    \item Developed a mobile version proof of concept for the A1 ERP. 
\end{itemize}
\techstack{Java, J2ME, PostgreSQL}
\vspace{0.8em}

\section{Education}
%=================%
\subsection{Jomo Kenyatta University of Agriculture and Technology $|$ {\normalfont\itshape Bsc. Computer Science} \hfill 2012}
\begin{itemize}
    \item Second Class Honors, Upper Division
    \item Coursework: Computer Programming, Data Structures and Algorithms, Database Management, Computer Security
\end{itemize}


\section{Certification \& Awards}
%===============================%
\begin{enumerate}[label=\null, left=0pt..0pt, itemsep=0pt]
    \item Kotlin for Java Developers, Coursera. \hfill 2019
\end{enumerate}

\end{document}
