\documentclass[11pt]{article} % fontsize 10pt/11pt/12pt

\usepackage[margin=1in, a4paper]{geometry}
\setcounter{secnumdepth}{0} % remove section numbering
\usepackage{titlesec}
\titlespacing{\subsection}{0pt}{*0}{*0} % remove vertical spacing above and below
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\large\itshape}
\usepackage{enumitem}
\setlist[itemize]{noitemsep,left=0pt .. \parindent}
\pagestyle{empty} % remove page number
\pdfgentounicode=1


\begin{document}

\begin{center}
    \begin{minipage}{0.5\textwidth}
    {\Huge\bfseries
        Nickson Kaigi
        } \\ \medskip
        Software Engineer
    \end{minipage} \hfill
    \begin{minipage}{0.4\textwidth}
        \raggedleft
        Email: nickaigi@gmail.com \\
        Mobile: +254 724 708 852 \\
        LinkedIn: linkedin.com/in/nickson-kaigi \\
        GitHub: github.com/nickaigi
    \end{minipage}
\end{center}

\section{Professional Summary}
Software engineer, with over a decade of experience working with Python. Driven individual, with a background in Computer Science and vast experience developing and shipping software and data products.

\section{Experience}

%\begin{itemize}
%        \item Beginning with your most recent position, describe your experience, skills, and resulting outcomes in bullet or paragraph form.
%        \item Begin each line with an action verb and include details that will help the reader understand your accomplishments, skills, knowledge, abilities, or achievements.
%        \item Quantify where possible. Do not use personal pronouns; each line should be a phrase rather than a full sentence.
%\end{itemize}

%\begin{itemize}
%        \item XYZ method - Accomplished [X] as measured by [Y], by doing [Z].
%        \item CAR method - Context, Action, Result. 
%        \item STAR method - Situation, Task, Action, Result.
%        \item Be consistent with headers and sub-headers. 
%\end{itemize}

%=================%
\subsection{SKUify Limited \hfill Nottinghamshire, England - Remote}
\subsubsection{Full Stack Engineer \hfill  December 2023 - December 2024}
\begin{itemize}
    \item Contributed to the successful development of the SKUify SaaS, enhancing inventory management and pricing optimization for Amazon and Arbitrage sellers, resulting in improved user engagement and operational efficiency.
    \item Succesfully migrated big tables used by the project to PostgreSQL partitioned tables, resulting in quicker query execution and improving API load times.

    \paragraph{Project Tech Stack:} Python, Django, Django REST Framework, React, PostgreSQL, Celery, Jenkins
\end{itemize}

\subsection{FreeCast Inc \hfill Florida, United States of America - Remote}
\subsubsection{Back-end Engineer \hfill  September 2022 - November 2023}
\begin{itemize}
    \item Contributed to the successful transition of the FreeCast APIs from Django REST Framework to FastAPI, increasing the number of Requests per Second (RPS) that the project could handle.
    \paragraph{Project Tech Stack:} Python, FastAPI, Django, Django REST Framework, MySQL, Docker, GitHub Actions
\end{itemize}

\subsection{Sum Software Limited \hfill Nottinghamshire, England - Remote}
\subsubsection{Full Stack Engineer \hfill  November 2021 - July 2022}
\begin{itemize}
    \item Contributed to the successful development of the "Journey" component of the Sumfully SaaS, enhancing inventory management for Amazon and Arbitrage sellers, resulting in improved operational efficiency.

    \paragraph{Project Tech Stack:} Python, Django, Django REST Framework, React, PostgreSQL, Celery, Jenkins
\end{itemize}


\subsection{World Bank Group \hfill Washington DC, United States of America - Remote}
\subsubsection{Technical Consultant \hfill  December 2021 - January 2022}
\begin{itemize}
    \item Contributed to the successful development of the Personal Case Based Teaching (PCBT) prototype that aimed to analyze past judgements in courts of law in a bid to determine judgemental bias.

    \paragraph{Project Tech Stack:} Python, Django, Django REST Framework, React, PostgreSQL, Celery, Jenkins
\end{itemize}


\subsection{Maxum Data Limited \hfill Auckland, New Zealand - Remote}
\subsubsection{Lead Developer \hfill  June 2015 - October 2021}
\begin{itemize}
    \item Contributed to the successful development of the mPort project that tracked mobile phone number portability across mobile network operators in New Zealand.
    \item Succesfully developed a search tool for custom Toll Free numbers that lead to an increase in toll free number uptake from users.
    \item Developed Lua scripts that allowed customization of Freeswitch. 

    \paragraph{Project Tech Stack:} Python, Django, MySQL, Lua,
\end{itemize}

\section{Education}
%=================%
\subsection{University of Post Graduation, City $|$ {\normalfont\itshape Degree Name} \hfill 2024}
\begin{itemize}
        \item Cumulative GPA: 3.69
        \item \textit{magna cum laude} 
  \item Related Coursework: Computer Architecture, Database Management, Cybersecurity
\end{itemize}


\section{Certification \& Awards}
%===============================%
\begin{enumerate}[label=\null, left=0pt..0pt, itemsep=0pt]
        \item Some programming bootcamp, Location. \hfill 2023
        \item Forbes Top 15 Procrastinators under 15. \hfill 2022
        \item Perticipation award for attending workshop. \hfill 2021
\end{enumerate}

\section{Skills \& Interests}
%===========================%
\begin{description}[itemsep=0pt]
        \item[Technical] List computer software and programming languages
        \item[Language] List foreign languages and your level of fluency
        \item[Laboratory] List scientific / research lab techniques or tools [If Applicable]
        \item[Interests] List activities you enjoy that may spark interview conversation
\end{description}

\end{document}
